---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# virtualclust

<!-- badges: start -->
<!-- badges: end -->

The goal of virtualclust is to ...

## Installation

You can install the development version of virtualclust like so:

``` r
# install.packages("devtools")
devtools::install_github("mncube/virtualclust")
```

## Example

This is a basic example which shows you how to solve simulate data where students are clustered within teachers and each student has a virtual comparison formed from summarizing a many-to-one match.

After simulating data we summarize the results from different statistical models.

```{r example}
library(virtualclust)

set.seed(123)
sim_data <- sim_tc_cv(n_treatment = 100, n_control = 1000, n_matches = 10)
head(sim_data$combined_data)

summary_results <- vc_summary(sim_data)
head(summary_results)
```
